---
title: "MK9 workflow"
author: "Sean Rohan"
date: "1/24/2022"
output: html_document
---

*WARNING: DO NOT KNIT THIS DOCUMENT! Run chunks individually.*

# Introduction

This markdown document contains code used for processing and aligning irradiance data collected using trawl-mounted archival tags (Wildlife Computers TDR-MK9) during AFSC bottom trawl surveys. This code should be run for one vessel/cruise combination at a time.

## 1. Setup local processing directory

Create a new directory for processing data.

```{r setup, include=TRUE, eval=FALSE}
library(trawllight)

channel <- trawllight:::get_connected(schema = "AFSC")
vessel <- 143 # Replace with vessel
cruise <- 201801 # Replace with cruise
survey <- "AI" # Region ("BS", "NBS", "GOA", "AI", or "SLOPE")

# Setup directory
source_path <- "G:/RACE_LIGHT/LightData/Data/year_18/ai/v_143/" # Replace with the source directory
trawllight::mk9_setup_dir(source_path = source_path,
                          overwrite = TRUE,
                          survey = survey,
                          vessel = vessel,
                          cruise = cruise)
```
## 2. Decode .wch file

Use WC-DAP software to decode binary (.wch) files and setup input csv files, as described in [0_decode_mk9.Md](/0_decode_mk9.Md).

## 3. Offset

```{r offset, include=TRUE, eval=FALSE}
trawllight::mk9_time_offset(channel = channel,
                        survey = survey,
                        cruise = cruise,
                        vessel = vessel)
```

## 4. Retrieve haul events and set up cast times

```{r casttimes, include=TRUE, eval=FALSE}
trawllight::mk9_cast_times(channel = channel,
                       survey = survey,
                       cruise = cruise,
                       vessel = vessel)
```

## 5. Align data and write output to CSV

```{r extinction, include=TRUE, eval = FALSE}
trawllight::mk9_extinction(channel = channel,
                       survey = survey,
                       cruise = cruise,
                       vessel = vessel)
```

## 6. Move to storage

Move the processed files to the storage directory.